---
title: "week 6 - overview"
author: "Scott Gee"
date: "30/03/2021"
output: 
  html_document:
    css: "www/style.css"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

<script src="www/hideOutput.js"></script>

<script src="www/hideOutput.js"></script>

For this week, the main thing you'll need to use are `mutate`, `group_by`, `summarise` and the pivot functions, `pivot_wider' and `pivot_longer`.

When getting the rankings of earnings, you need to get the overall rank and the specific tour rank like:

```{r, eval=FALSE}
dataframe %>% 
  mutate(overall_rank = rank(desc(earnings_column))) %>% 
  group_by(tour_column) %>% 
  mutate(tour_rank = rank(desc(earnings_column)))
```

After you have done the calculations you need to pivot the data in to the required format. I think this is easiest by first pivoting from wide to long and then from long to wide again like

```{r, eval=FALSE}
calculation_dataframe %>% 
  pivot_longer(-tour_column) %>% 
  pivot_wider(names_From = tour_column, values_from = value)
```

