---
title: "week 3 - solutions"
author: "Scott Gee"
date: "22/03/2021"
output: 
  html_document:
    css: "www/style.css"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
<script src="www/hideOutput.js"></script>

Load libraries and read in data (this also answers question 3)
<div class="fold s">
```{r load-libraries, message=FALSE, warning=FALSE}
library(tidyverse)
library(readxl)
library(lubridate)
library(data.table)

sheet_names <- excel_sheets('data.xlsx')

sheet_names <- set_names(sheet_names, sheet_names) #this ensures that we can use an id column as the store name

dat <- map_df(sheet_names, ~ read_excel('data.xlsx', sheet = .x), .id = 'store')
```
</div>
*1*. Pivot new and existing and split into customer type and product

<div class="fold h">
```{r}
# Use pivot_longer and then separate 
```
</div>
<div class="fold s o ">
```{r pivot-new-existing}
dat_q1 <- dat %>% 
  pivot_longer(`New - Saddles`:`Existing - Bags`, names_to = 'product_type', values_to = 'sales') %>% 
  separate(product_type, into = c('customer_type', 'product')) 
  
```
</div>
*2*. Rename `sales` to `Products Sold`
<div class="fold s o">
```{r rename-column}
dat_q2 <- rename(dat_q1, `Products Sold` = sales)

```
</div>
*3*. Create a `store` column name (done in setup)

*4*. Remove any unneceessary columns (not needed here for R)

*5*. Turn `date` into `quarter`
<div class="fold s">
```{r}
dat_q5 <- mutate(dat_q2, quarter = quarter(Date))
```
</div>
*6*. Get aggregated products sold by:
`Product`, `Quarter`
<div class="fold s">
```{r aggregate-1}
dat_q6_1 <- dat_q5 %>% 
  group_by(product, quarter) %>% 
  summarise(`Products Sold` = sum(`Products Sold`))

```
</div>
`Store`, `Customer Type`, `Product`
<div class="fold s o ">

```{r aggregate-2}
dat_q6_2 <- dat_q5 %>% 
  group_by(store, customer_type, product) %>% 
  summarise(`Products Sold` = sum(`Products Sold`))
```
</div>

Export data 

<div class="fold s">
```{r}
fwrite(dat_q6_1, file = 'correct-output-1.csv')

fwrite(dat_q6_2, file = 'correct-output-2.csv')
```
</div>

These could both be written within one pipe like the below

<div class="fold s o ">
```{r one-pipe}
dat %>% 
  pivot_longer(`New - Saddles`:`Existing - Bags`, names_to = 'product_type', values_to = 'sales') %>% 
  separate(product_type, into = c('customer_type', 'product')) %>%
  rename(`Products Sold` = sales) %>% 
  mutate(quarter = quarter(Date)) %>% 
  group_by(product, quarter) %>% 
  summarise(`Products Sold` = sum(`Products Sold`)) 

dat %>% 
  pivot_longer(`New - Saddles`:`Existing - Bags`, names_to = 'product_type', values_to = 'sales') %>% 
  separate(product_type, into = c('customer_type', 'product')) %>%
  rename(`Products Sold` = sales) %>% 
  mutate(quarter = quarter(Date)) %>%
  group_by(store, customer_type, product) %>% 
  summarise(`Products Sold` = sum(`Products Sold`))
```
</div>
