---
title: "week4 - solutions"
author: "Scott Gee"
date: "23/03/2021"
output: 
  html_document:
    css: "www/style.css"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

<script src="www/hideOutput.js"></script>

Load libraries and read in data.

*1*. Bind data together with `map_df`
<div class="fold s">
```{r load-libraries, message=FALSE, warning=FALSE}
library(tidyverse)
library(readxl)
library(lubridate)
library(data.table)

sheet_names <- excel_sheets('data.xlsx')[1:5]

sheet_names <- set_names(sheet_names, sheet_names) #this ensures that we can use an id column as the store name

dat <- map_df(sheet_names, ~ read_excel('data.xlsx', sheet = .x), .id = 'store')
```
</div>

*2*. Pivot product columns
<div class="fold h">
```{r}
# Use pivot_longer
```
</div>
<div class="fold s">
```{r pivot}
dat_q2 <- pivot_longer(dat, `New - Saddles`:`Existing - Bags`)
```
</div>
*3*. Split field with customer type and product and rename `value` column to products sold
<div class="fold s">
```{r split-field}
dat_q3 <- separate(dat_q2, name, into = c('customer_type', 'product'), sep = ' - ')

dat_q3 <- rename(dat_q3, products_sold = value)
```
</div>
*4*. Turn the `date` into a `quarter`
<div class="fold s">
```{r date-quarter}
dat_q4 <- mutate(dat_q3, quarter = quarter(Date))
```
</div>
*5*. Sum up products sold by `store` and `quarter`
<div class="fold s">
```{r sum-products}
dat_q5 <- dat_q4 %>% 
  group_by(store, quarter) %>% 
  summarise(products_sold = sum(products_sold))
```
</div>
*6*. Add targets data
<div class="fold s">
```{r add-targets}
targets <- read_excel('data.xlsx', sheet = 'Targets')
```
</div>
*7*. Join `targets` data to aggregated stores data
<div class="fold h">
```{r}
# Use inner_join
```
</div>
<div class="fold s">
```{r join, message=FALSE}
dat_q7 <- inner_join(dat_q5, targets, by = c('store' = 'Store', 'quarter' = 'Quarter'))
```
</div>
*8*. No need to remove duplicates

*9*. Calculate variance between actual sales and target

<div class="fold s">
```{r calculate-variance, message=FALSE}
dat_q9 <- mutate(dat_q7, variance_to_target = Target - products_sold)
```
</div>

*10*. Rank the stores based on variance to target in each quarter
<div class="fold h">
```{r}
# group_by the quarter and then use rank in desc order 
```
</div>
<div class="fold s">
```{r rank-stores}
dat_q10 <- dat_q9 %>% 
  group_by(quarter) %>% 
  mutate(rank = rank(desc(variance_to_target)))
```
</div>

*11*. Export data

<div class="fold s">
```{r export}
fwrite(dat_q10, 'correct-output.csv')
```
</div>

You could write this within one pipe call with the below:

<div class="fold s">
```{r one-pipe}
one_pipe <- dat %>% 
  pivot_longer(`New - Saddles`:`Existing - Bags`) %>% 
  separate(name, into = c('customer_type', 'product'), sep = ' - ') %>% 
  rename(products_sold = value) %>% 
  mutate(quarter = quarter(Date)) %>% 
  group_by(store, quarter) %>% 
  summarise(products_sold = sum(products_sold)) %>% 
  inner_join(targets, by = c('store' = 'Store', 'quarter' = 'Quarter')) %>% 
  mutate(variance_to_target = Target - products_sold) %>% 
  group_by(quarter) %>% 
  mutate(rank = rank(desc(variance_to_target))) 
    
```
</div>
