---
title: "week 12 - solutions"
author: "Scott Gee"
date: "01/04/2021"
output: 
  html_document:
    css: "www/style.css"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

<script src="www/hideOutput.js"></script>

Load libraries and read in data
<div class="fold s">
```{r, message=FALSE, warning=FALSE}
library(tidyverse)
library(readxl)
library(data.table)

dat <- read_excel('data.xlsx')

```
</div>
*1*. Pivot all of the month fields in to a single column (can ignore warnings, these are coming as there are months with NAs)
<div class="fold h">
```{r, eval=FALSE}
# You'll need to make the columns that you want to pivot the same type (numeric), this can be done with the below

dat %>% 
  replace(is.na(.), NA_integer_) %>% 
  mutate(across(starts_with('01'), as.numeric)) 
```
</div>
<div class="fold s">
```{r, warning=FALSE}
dat_q1 <- dat %>% 
  replace(is.na(.), NA_integer_) %>% 
  mutate(across(starts_with('01'), as.numeric)) %>% 
  pivot_longer(`01-01-10`:`01-12-20`)
```
</div>

*2*. Filter out the nulls
<div class="fold s">
```{r}
dat_q2 <- filter(dat_q1, !is.na(value))
```
</div>
*3*. Filter to only include values that unit value is number of tourists
<div class="fold s">
```{r}
dat_q3 <- filter(dat_q2, `Unit-Detail` == 'Tourists')
```
</div>
*4*. Get the number of tourists from each country for each month. If you have the continent but not the country, albel the country as *Unknown*.
<div class="fold h">
```{r}
# Remove all measures that are not tourist arrivals (look at hierarchy breakdown column)
# Create a country/origin and continent column using the hierarchy breakdown column
# Create two separate dataframes, one where you know the country and one where you don't, with arrivals by continent. 
# Bind the unknown country dataframe with a dataframe that is the monthly arrivals by country with continent included as a column
```
</div>
<div class="fold s">
```{r}
dat_q4 <- dat_q3 %>% 
  filter(str_detect(`Hierarchy-Breakdown`, 'Tourist arrivals')) %>% 
  mutate(origin = str_remove(`Series-Measure`, 'Tourist arrivals from '),
         continent = if_else(str_remove(`Hierarchy-Breakdown`, 'Real Sector / Tourism / Tourist arrivals / ') == 'Real Sector / Tourism / Tourist arrivals',
                             origin,
                             str_remove(`Hierarchy-Breakdown`, 'Real Sector / Tourism / Tourist arrivals / '))) %>% 
  select(origin, continent, name, value) 

total_known_country <- dat_q4 %>% 
  filter(origin != continent) %>% 
  group_by(continent, name) %>% 
  summarise(known = sum(value)) 

total_unknown_country <- dat_q4 %>% 
  filter(origin == continent) %>% 
  select(continent, name, value) %>% 
  rename(total = value)

unknown_country <- left_join(total_unknown_country, total_known_country, by = c("continent", "name")) %>% 
  mutate(value = total - known) %>% 
  select(continent, name, value) %>% 
  mutate(country = 'Unknown')

dat_q4_final <- dat_q4 %>% 
  filter(origin != continent) %>% 
  rename(country = origin) %>% 
  rbind(unknown_country) %>% 
  rename(Breakdown = continent,
         `Number of Tourists` = value,
         Month = name,
         Country = country) %>% 
  select(Breakdown, `Number of Tourists`, Month, Country) 

```
</div>

*5*. Output
<div class="fold s">
```{r}
fwrite(dat_q4_final, 'correct-output.csv')
```
</div>