---
title: "week 10 - solutions"
author: "Scott Gee"
date: "31/03/2021"
output: 
  html_document:
    css: "www/style.css"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

<script src="www/hideOutput.js"></script>

Load libraries and read in data
<div class="fold s">
```{r, message=FALSE, warning=FALSE}
library(tidyverse)
library(readxl)
library(writexl)
library(scales)
library(data.table)
library(janitor)

pokemon <- read_excel('data.xlsx', sheet = 'pokemon')

evolution <- read_excel('data.xlsx', sheet = 'evolution')
```
</div>
*1*. Remove records with `Number` higher than 386 and those that start with Mega

<div class="fold h">
```{r}
# You can use the str_starts function from stringr
```
</div>

<div class="fold s">
```{r}
pokemon_q1 <- filter(pokemon, Number <= 386,
                              !str_starts(Name, 'Mega'))
```
</div>

*2*. Some Pokémon have more than one Type. We aren't interested in Types for this challenge so remove this field and ensure we have one row per Pokémon.
<div class="fold h">
```{r}
# Use distinct
```
</div>
<div class="fold s">
```{r}
pokemon_q2 <- pokemon_q1 %>% 
  select(-Type) %>% 
  distinct()
```
</div>
*3*. Bring in information about what our Pokémon evolve to

<div class="fold h">
```{r}
# Remove duplicates before joining with distinct
```
</div>
<div class="fold s">
```{r}
evolution_q3 <- distinct(evolution)

dat_q3 <- left_join(pokemon_q2, evolution_q3, by = c('Name' = 'Evolving from')) 

```
</div>

*4*. Bring in information about what a Pokémon evolves from
<div class="fold s">
```{r}
dat_q4 <- left_join(dat_q3, evolution_q3, by = c('Name' = 'Evolving to')) 
```
</div>
*5*. Create an `evolution_group` column which shows the first evolution of a pokemon for each name.

<div class="fold h">
```{r}
# Good luck
```
</div>
<div class="fold s">
```{r}
original_name <- dat_q4 %>% 
  select(Name, `Evolving to`, `Evolving from`)  %>% 
  mutate(original = if_else(is.na(`Evolving from`) == TRUE, 1,0)) %>% 
  filter(original == 1) %>% 
  rename(original_name = Name) %>% 
  select(original_name) 


evolution_groups <- original_name  %>% 
  left_join(dat_q4 %>% select(Name, `Evolving to`, `Evolving from`),
            by = c('original_name' = 'Evolving from')) %>% 
  mutate(evolution_group = original_name) %>% 
  rename(evolution_1 = Name,
         evolution2 = `Evolving to`) %>% 
  pivot_longer(-evolution_group) %>% 
  filter(!is.na(value)) %>% 
  distinct() 

dat_q5 <- left_join(dat_q4, evolution_groups, by = c('Name' = 'value')) %>% 
  mutate(evolution_group = if_else(is.na(evolution_group) == TRUE, `Evolving from`, evolution_group))
```
</div>

*6*. Some duplication may have occurred with all our joins, ensure no 2 rows are exactly the same (not needed)

*7*. Output 
<div class="fold s">
```{r}
dat_q5 %>% 
  select(evolution_group, 
         Number, 
         Name, 
         Total,
         HP, 
         Attack,
         Defense,
         `Special Attack`,
         `Special Defense`,
         Speed,
         `Evolving from`,
         `Evolving to`,
         Level.x,
         Condition.x,
         `Evolution Type.x`) %>% 
  rename(Level = Level.x,
         Condition = Condition.x,
         `Evolution Type` = `Evolution Type.x`) %>% 
  fwrite('correct-output.csv')
```
</div>
