---
title: "week 2 - solutions"
author: "Scott Gee"
date: "22/03/2021"
output: 
  html_document:
    css: "www/style.css"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
<script src="www/hideOutput.js"></script>

Load libraries and read in data
<div class="fold s">
```{r load-libraries, message=FALSE,warning=FALSE}
library(tidyverse)
library(readxl)
library(writexl)

dat <- read_excel('data.xlsx')
```
</div>
*1*. Clean up the `model` field to leave only the letters
<div class="fold s">
```{r clean-model-field}
dat_q1 <- mutate(dat, Brand = str_extract(Model, "[aA-zZ]+"))
```
</div>
*2*. Work out order value 
<div class="fold s">
```{r order-value}
dat_q2 <- mutate(dat_q1, order_value = Quantity * `Value per Bike`)
```
</div>
*3*. Aggregate quantity sold, order value, average value by brand and bike type 
<div class="fold s">
```{r aggregate-1}
dat_q3 <- dat_q2 %>% 
  group_by(`Bike Type`, Brand) %>% 
  summarise(quantity_sold = sum(Quantity), 
            order_value = sum(order_value),
            average_value = mean(sum(order_value)/sum(Quantity)))
```
</div>
*4*. Calculate days to ship
<div class="fold s">
```{r days-to-ship}
dat_q4 <- dat_q2 %>% 
  mutate(days_to_ship = `Shipping Date`- `Order Date`)
```
</div>
*5*. Aggregate order value, quantity sold and average days to ship by brand and store
<div class="fold s">
```{r aggregate-2}
dat_q5 <- dat_q4 %>% 
  group_by(Brand, Store) %>% 
  summarise(quantity_sold = sum(Quantity), 
            order_value = sum(order_value),
            average_shipping_time = as.numeric(mean(days_to_ship)))
```
</div>

*6*. Round to 1 decimal place
<div class="fold s">
```{r round}
dat_q6_1 <- mutate(dat_q5, across(where(is.numeric), round, 1))

dat_q6_2 <- mutate(dat_q3, across(where(is.numeric), round, 1))
```
</div>
*7*. Output
<div class="fold s">
```{r export}
export_data <- list(dat_q6_1, dat_q6_2)

write_xlsx(export_data, path = 'correct-output.xlsx', format_headers = FALSE)
```
</div>
Both of these could be written within one pipe by chaining the statements.
<div class="fold s">
```{r one-pipe}
dat %>% 
  mutate(Brand = str_extract(Model, "[aA-zZ]+"),
         order_value = Quantity * `Value per Bike`) %>% 
  group_by(`Bike Type`, Brand) %>% 
  summarise(quantity_sold = sum(Quantity), 
            order_value = sum(order_value),
            average_value = mean(sum(order_value)/sum(Quantity))) %>% 
  mutate(across(where(is.numeric), round, 1)) %>% 
  head()

dat %>% 
  mutate(Brand = str_extract(Model, "[aA-zZ]+"),
         order_value = Quantity * `Value per Bike`,
         days_to_ship = `Shipping Date`- `Order Date`) %>% 
  group_by(Brand, Store) %>% 
  summarise(quantity_sold = sum(Quantity), 
            order_value = sum(order_value),
            average_shipping_time = as.numeric(mean(days_to_ship))) %>% 
   mutate(across(where(is.numeric), round, 1)) %>% 
  head()
  
```
</div>
