---
title: "week 4 - overview"
author: "Scott Gee"
date: "30/03/2021"
output: 
  html_document:
    css: "www/style.css"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

<script src="www/hideOutput.js"></script>

In this weeks problem, the first few questions are very similar to last week so you can amend your answers slightly.

Once again you can use `map_df` to read in the files like this:

```{r, message=FALSE, warning=FALSE}

library(tidyverse)
library(readxl)

sheet_names <- excel_sheets('data.xlsx')[1:5] # get the first 5 sheet names (exclude the targets sheet)

sheet_names <- set_names(sheet_names, sheet_names) #name each object in the list with its name (helps for map_df)

dat <- map_df(sheet_names, ~ read_excel('data.xlsx', sheet = .x), .id = 'store') # read in each sheet using the sheet name and then bind in to one data frame, creating the store column which will use the name of the sheet
```

This is the first exercise that requires joins and this can be done with `dplyr` and the [`inner_join`](https://dplyr.tidyverse.org/reference/join.html) function. This is done in a very similar way to SQL, you just need to state the columns you are joining by in the `by =` argument.

After this you can use `mutate` and `group_by`, and `rank` from `dplyr` to answer the following questions. 