---
title: "week 7 - overview"
author: "Scott Gee"
date: "29/03/2021"
output: 
  html_document:
    css: "www/style.css"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
<script src="www/hideOutput.js"></script>
For this week, there's a lot of string manipulation which may be quite new to you.

There's a guide on strings [here](https://r4ds.had.co.nz/strings.html)

You'll need to convert a comma separated list in to a dataframe. It might be easier to split the `keywords` data in to the E numbers and animal ingredients part. `dplyr` has a function called `separate_rows` that will convert a separated list when you register the `sep` argument like `separate_rows(column, sep = " ,")`. After this you'll need to merge these two dataframes together.

In question 2, you need to check whether each product contains any non-vegan products. After you get a list of the strings that contain animal products, look at this [post](https://stackoverflow.com/questions/35962426/multiple-strings-with-str-detect-r)

For question 4 you need to create a column that is a comma separated list of the animal ingredients that are in a product. Use the below to get a list of the keywords with the names assigned to each keyword.

```{r, eval=FALSE}
#Get the keywords as a list of strings and name each string 
keywords_list <- pull(keywords_rows) %>% 
  set_names()
```

The next part is checking each string against the ingredients/allergens. The [`map`](https://r4ds.had.co.nz/iteration.html#the-map-functions) functions will be helpful for this, especially `map_df`. Something like this will work 

`shopping_dataframe_name %>% 
  mutate(map_df(keywords_list, ~ str_detect(ingredients_column, .x)))`
  
After this you'll want to pivot the data from wide to long with [`pivot_longer`](https://thatdatatho.com/tidyrs-pivot_longer-and-pivot_wider-examples-tidytuesday-challenge/), filter for only the TRUE columns, `group_by` the Product and then use `glue_collapse` to create the list.